---
title: "Bivariate Analysis"
author: "Maliat"
date: "10/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/malia/OneDrive/Desktop/710 Memos")
library(tidyverse)
library(magrittr)
library(foreign)
library(descr)
library(lubridate)
library(expss)
GSS <- read.dta("C:\\Users\\malia\\Downloads\\GSS1972_2014v12.dta")
```

```{r}
GSS$socclass<- cut(GSS$educ, c(0,11,12,99), labels=c("high school dropout","highschool graduate","at least some college"))
```

### views on anti-miscegenation on the basis of social class(education)
```{r}
GSS.1 <- GSS %>%
  select(year,socclass,racmar)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$socclass, GSS.1$racmar, prop.r = T, chisq = T, dnn=c("Social Class", "Views on anti-miscegenation laws on the basis of education"))
```

### views on anti-miscegenation  on the basis of race
```{r}
GSS.1 <- GSS %>%
  select(year,race,racmar)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$race, GSS.1$racmar, prop.r = T, chisq = T, dnn=c("Race", "Views on anti_miscegenation on the basis of race"))
```
### views on abortion on the basis of social class(education)
```{r}
GSS.1 <- GSS %>%
  select(year,socclass,abany)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$socclass, GSS.1$abany, prop.r = T, chisq = T, dnn=c("Social Class", "views on abortion on the basis of education"))
```
### views on abortion on the basis of race

```{r}
GSS.1 <- GSS %>%
  select(year,race,abany)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$race, GSS.1$abany, prop.r = T, chisq = T, dnn=c("race", "views on abortion on the basis of race "))
```
###views on African American's income inequality due to discrimination on the basis of education
```{r}
GSS.1 <- GSS %>%
  select(year,socclass,racdif1)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$socclass, GSS.1$racdif1, prop.r = T, chisq = T, dnn=c("social class", "views on African American's income inequality due to discrimination on the basis of education"))

```
###views on African American's income inequality due to discrimination on the basis of race
```{r}
GSS.1 <- GSS %>%
  select(year,race,racdif1)%>%
  filter(year %in% c("2000","2002","2004","2006","2008","2010","2012","2014"))
  crosstab(GSS.1$race, GSS.1$racdif1, prop.r = T, chisq = T, dnn=c("race", "views on African American's income inequality due to discrimination on the basis of race"))

```